---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

# Question 1:

 Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.


```{r}
codeclan_tweets <- read_csv("data/code_clan_tweets.csv")
```

```{r}
dim(codeclan_tweets)
names(codeclan_tweets)
#view(codeclan_tweets)
#glimpse(codeclan_tweets)
```
# Question 2:

Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
codeclan_tweets %>% 
  filter(is_quote == FALSE) %>% 
  summarise(favorite_count = sum(favorite_count))
```
# Question 3:

Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
codeclan_tweets %>% 
  filter(is_quote == FALSE) %>% 
  group_by (source) %>% 
  summarise(retweet_mean = mean(retweet_count))
```

# Question 4:

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.


```{r}
codeclan_tweets %>% 
  group_by(media_type) %>% 
  summarise(total_likes = sum(favorite_count)) %>% 
  mutate(media_type = if_else(is.na(media_type), "text", media_type)) %>% 
  arrange(desc(total_likes))



```

# Question 5: 

Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).



```{r}
?across
```





```{r}
codeclan_tweets %>% 
  select(text) %>%
  mutate(text_count = nchar(text), .after = text) %>% 
  summarise(mean_tweets = mean(text_count))
  
view(codeclan_tweets)
```
Just for checking if the value is acceptable...


```{r}
codeclan_tweets %>% 
  select(text) %>%
  mutate(text_count = nchar(text), .after = text) %>% 
  arrange(desc(text_count))
  
```

# Question 6:

The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
codeclan_info <- read_csv("data/code_clan_info.csv")
```


```{r}
#view(codeclan_info)
join <- left_join(codeclan_info, codeclan_tweets, by = "tweet_id")
join
```
# Question 7:

From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- join %>% 
          select(tweet_id, hashtags) %>% 
          mutate(hashtags = str_to_lower(hashtags)) %>% 
          filter(!is.na(hashtags))

codeclan_hashtags
```


## Extensions

# Question 8:

Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with charactersc(. 

```{r}
?str_detect()
```


```{r}
codeclan_hashtags %>%
  mutate(start_hashtags = str_sub(hashtags, end = 2),.after = hashtags) %>% 
  filter(str_detect(start_hashtags, "c\\("))
```

```{r}
?str_detect
```

