---
title: "Chiara homework week 6 day 3"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
library(janitor)
```


# 1 MPV

## Task 1:

Load the data again, clean_names(), and re-familiarise yourself with it



```{r}
ames <- clean_names(read_csv("data/ames.csv"))
```

```{r}
dim(ames)
names(ames)
```

## Task 2:

Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?


```{r}
ames %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(col = "white",
                 fill = "steelblue")
```


```{r}
ames %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_boxplot()
```

Having a first sight both of the histogram and of the boxplot, it seems that the distribution of lot_area is ruoghly right skewed


## Task 3:

Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_resample_ames <- ames %>% 
  specify(response = lot_area) %>% #specify the variable of interest
  generate(reps = 5000, type = "bootstrap") %>% #generate the replicate resamples
  calculate(stat = "mean") # calculate the statistic of interest for each resample


bootstrap_resample_ames
```

I've created a bootstrap sampling distribution for the mean of lot_area.

Now I am going to visualise it.

```{r}
bootstrap_resample_ames %>% 
  ggplot() +
  aes(x = stat) +
  geom_histogram(colour = "white", 
                 fill = "purple")
```


As we expected, the distribution seems very similar to the normal distribution!


## Task 4:

Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution


```{r}
infer_ci_95 <- bootstrap_resample_ames %>% 
  get_ci(level = 0.95, type = "percentile")
#level adjust CI, type adjust type of CI
infer_ci_95
```

```{r}
bootstrap_resample_ames %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95)
```


```{r}
mean_bootstrap <- bootstrap_resample_ames %>% 
  summarise(mean = mean(stat))

mean_bootstrap
```
```{r}
mean_95 <- bootstrap_resample_ames %>%
  filter(stat >= 9875 & stat <= 10451) %>% 
  summarise(mean = mean(stat))

mean_95
```




## Task 5:

You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
infer_ci_99 <- bootstrap_resample_ames %>% 
  get_ci(level = 0.99, type = "percentile")
#level adjust CI, type adjust type of CI
infer_ci_99
```


```{r}
bootstrap_resample_ames %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99)
```

```{r}
mean_99 <- bootstrap_resample_ames %>%
  filter(stat >= 9810 & stat <= 10548) %>% 
  summarise(mean = mean(stat))

mean_99
```

Using the 99% CI we obtain an roughly higher value for the mean of lot_area!


## Task 6:

 Calculate the point estimate of the mean(lot_area)


```{r}
mean_bootstrap <- bootstrap_resample_ames %>% 
  summarise(mean = mean(stat))

mean_bootstrap
```

# Extension

## Task 1:

Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting].

```{r}
ames_1920 <- ames %>% 
  filter(yr_sold <= 1920)
```


```{r}
#200 reps

ames_1920_resample_200 <- ames_1920 %>% 
  specify(response = lot_area) %>% 
  generate(reps = 200, type = "bootstrap") %>% 
  calculate(stat = "mean") 


#3000 reps
ames_1920_resample_3000 <- ames_1920 %>% 
  specify(response = lot_area) %>% 
  generate(reps = 3000, type = "bootstrap") %>% 

```









































































