---
title: "R Notebook"
output: html_notebook
---

```{r}
library(gtools)
library(tidyverse)
library(stringr)
library(janitor)
source("prob.R")
```

#1.1 The Titanic


```{r}
titanic <- read_csv("data/titanic.csv")
```
```{r}
titanic %>% 
  distinct(class)
```

```{r}
titanic_info <- titanic %>% 
  mutate(class = if_else(class %in% c("1st", "2nd", "3rd"), "passenger", "crew"))

titanic_info %>% 
  distinct(class)
```


```{r}
survived_table <- titanic_info %>% 
  tabyl(class, survived) %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all")

survived_table
```
Let's check if the events A (the person is a crew member/passenger) and B(the person is survived are or not dependent)



```{r}
p_crew <- 0.4032623

p_survived <- 0.32215677

p_survived_and_crew <- 0.09560489

p_crew * p_survived


```

```{r}
p_pass <- 0.5967377

p_survived <- 0.32215677

p_survived_and_pass <- 0.22655188

p_pass * p_survived
```
The events 'be a passenger' / 'be survived' and "be a crew member" / "be survived" are respectively dependent

$$p(survived | crew) = P(survived \cap crew) / p(crew)$$ 
```{r}
p_survived_given_crew <- p_survived_and_crew / p_crew

p_survived_given_crew
```

```{r}
p_survived_given_pass <- p_survived_and_pass / p_pass

p_survived_given_pass
```
The passenger survived are more than the crew members survived!


```{r}
prob_crew <- titanic_info %>% 
  summarise(prob = sum(class == "crew") / n()) %>% 
  pull()

prob_crew
p_crew
```


```{r}
prob_pass <- titanic_info %>% 
  summarise(prob = sum(class == "passenger") / n()) %>% 
  pull()

prob_pass
p_pass
```

```{r}
prob_survived <- titanic_info %>% 
  summarise(prob = sum(survived == "yes") / n()) %>% 
  pull()

prob_survived
p_survived
```
```{r}
prob_survived_and_crew <- titanic_info %>% 
  filter(class == "crew", survived == "yes") %>% 
  summarise(prob = n() / nrow(titanic_info)) %>% 
  pull()

prob_survived_and_crew
p_survived_and_crew
```
```{r}
prob_survived_and_pass <- titanic_info %>% 
  filter(class == "passenger", survived == "yes") %>% 
  summarise(prob = n() / nrow(titanic_info)) %>% 
  pull()

prob_survived_and_pass
p_survived_and_pass
```

```{r}
prob_survived_given_crew <- prob_survived_and_crew / prob_crew

prob_survived_given_crew
```

```{r}
prob_survived_given_pass <- prob_survived_and_pass / prob_pass

prob_survived_given_pass
```

#1.2 Probability Consolidation Questions

## Question 1

 If I roll a six-sided dice once, what is the probability of getting a number less than 5?
 
 S(roll a six-sided dice once) = {1, 2, 3, 4, 5, 6}
 
 Event A: getting a number less than 5 -> {1, 2, 3, 4}
 
 So, the probability is P(A) = 4 / 6 = 2 / 3 = 0.6666667
 
 
 Let's do it with dplyr:
 
```{r}
space_roll_die <- rolldie(1, 6) 

space_size <- space_roll_die %>% 
  summarise(space_size = n()) %>% 
  pull()

num_less_than_5 <- space_roll_die %>% 
  filter(X1 < 5) %>% 
  summarise(size_event_space = n()) %>% 
  pull()


prob <- num_less_than_5 / space_size
prob
```
 

## Question 2:

 How many outcomes are there in the sample space of an experiment in which we toss three dice?
 
```{r}
6^3
```
```{r}
sample_space <- rolldie(3, 6)

card_sample_space <- sample_space %>% 
  summarise(card = n()) %>% 
  pull()

card_sample_space
```
 
## Question 3:

In an experiment where we roll four dice:

  a) how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?
  b) what is the probability of this event?
  c) what assumptions do we apply in answering part ii?
  

### a)

A: the total of the four dice is 5, 6 or 7


```{r}
#outcomes A
s_four_dice <- rolldie(4, 6)

outcomes_a <- s_four_dice %>% 
  filter((X1 + X2 + X3 + X4) %in% c(5, 6, 7)) %>% 
  summarise(outcomes = n()) %>% 
  pull()

outcomes_a

```
There are 34 possible outcomes for the event A

### b)

  
```{r}
sample_size <- 6^4

s_four_dice <- rolldie(4, 6)

s_four_dice %>% 
  summarise(size = n()) %>% 
  pull() # just for verifying that it's equal to 6^4 and it is!!!
```
```{r}
p_a <- outcomes_a / sample_size
p_a
```
```{r}
prob_a <- s_four_dice %>% 
  filter((X1 + X2 + X3 + X4) %in% c(5, 6, 7)) %>% 
  summarise(prob = n() / nrow(s_four_dice)) %>% 
  pull()

prob_a
p_a
```
P(A) = 0.02623457

### c) 

We assume that the three events 
  A_1: the total of the four dice is 5,
  A_2: the total of the four dice is 6,
  A_3: the total of the four dice is 7
are independent.


## Question 4:

Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?


```{r}
#p(ordered_chairs) = 1/5!
p <- 1 / (5*4*3*2)
p
```

## Question 5:

I roll six dice:

  -  what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
  
```{r}
sample_size <- 6^6

p <- 1/sample_size
p
```
  
  -  what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?


```{r}
p <- (6*5*4*3*2)/sample_size
p
```

## Question 6:

 If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades? 
 
```{r}
p <- 13/ 52
p
```
 









