---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack <- backpack
```

#MVP

## Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.

```{r}
names(backpack)
```
Here we have a list of the variables involved in the 'backpack' dataset. There are 9 variables in total.

```{r}
dim(backpack)
```

We have 100 entries for these 9 variables.

```{r}
glimpse(backpack)
```
Here we have a look at the characteristics of each column. Type 'fct' means a factor/categorical variable.


## Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
backpack %>% 
  arrange(desc(backpack_weight))
```


```{r}
backpack %>% 
  ggplot()+
  aes(x = backpack_weight) +
  geom_bar(fill = "gold") +
  scale_x_continuous(breaks = 1:35)
```

I think that s bar-chart gives a good idea of the distribution of the backpack weights of the students of our dataset.
In the x axis we can see all the possible weights, and each bar is much longer depending on the number of backpacks with that weight in the dataset.


## Question 3.

Are there differences in backpack weight between sex?


```{r}
backpack %>% 
  ggplot()+
  aes(x = backpack_weight, fill = sex) +
  geom_histogram(bins = 20, col = "white") +
  scale_x_continuous(breaks = 1:35) +
  facet_wrap(~sex, nrow = 2)
```
In this chart we can see the distribution of each weight depending on sex.

```{r}
backpack %>% 
  ggplot()+
  aes(x = sex, y = backpack_weight, fill = factor(backpack_weight)) +
  geom_col(position = "dodge") 
```


In this chart, for each sex we can see the number of backpacks for each weight.


## Question 4.

What is the relationship between body weight and backpack weight?


```{r}
backpack %>% 
   ggplot()+
  aes(x = backpack_weight, y = body_weight) +
  geom_point() +
    geom_smooth(method = lm)

```

This chart gives me a general overview of the relation between backpack weights and body weights.




## Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.


```{r}
backpack %>% 
   ggplot()+
  aes(x = backpack_weight, y = body_weight, colour = sex) +
  geom_point() +
    geom_smooth(method = lm) 

```

The trend of the relationship is more or less the same between men and women. However, of course, women has in general a weight trend line lower with respect to men.


## Question 6.

What proportion of students report back pain?


```{r}
backpack <- backpack %>%
  mutate(backpain_labelled = recode(back_problems, 
                       "0" = "No", 
                       "1" = "Yes"))

backpack %>% 
  ggplot() +
  aes(x = back_problems, fill = factor(back_problems)) +
  geom_bar()+
  scale_x_continuous(breaks = 0:1) +
  theme(legend.position = "none") +
  labs(x = "Backpain (0/1)",
       y = "Number of students",
       )

backpack %>% 
  ggplot(aes(x = factor(back_problems), fill = sex)) +
  geom_bar(position = "fill")

```



```{r}
backpack1 <- backpack %>% 
  mutate(back_problems = recode(back_problems,
                               "1" = "Back problem",
                                "0" = "No back problem"))



backpack1 %>% 
ggplot(aes(x = back_problems, y = after_stat(prop), group = 1)) +
  geom_bar() +    
  xlab("Back issues among students") +
  ylab("Percentage") +
  ggtitle("Percentage students with back issues") +
  scale_y_continuous(labels = scales::percent_format())
```


```{r}
backpack %>% 
  ggplot(aes(x = "", fill = back_problems)) +
  geom_bar(position = "fill") +
  theme_minimal() +
  labs(y = "proportion",
       x = "proportion of students with back pain") +
  scale_y_continuous(labels = scales::percent)
```







This chart gives us the count of students who has back problems and the count of students who doesn't.

## Question 7.

Is this proportion different between men and women?



```{r}
backpack %>% 
  ggplot() +
  aes(x = back_problems, fill = factor(back_problems)) +
  geom_bar()+
  scale_x_continuous(breaks = 0:1) +
  facet_wrap(~sex) +
  theme(legend.position = "none")
```
This chart compare the number of students with back problems with the number of students without back problems for both the two sexes.

## Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.


```{r}
backpack %>% 
  ggplot() +
  aes(x = backpack_weight, y = body_weight, colour = factor(back_problems)) +
  geom_point(position = "dodge") +
  facet_grid(sex~back_problems) +
  geom_smooth(method = lm)

```

Here we show the relationship between backpack weight and body weight depending on gender and on back problems.

#Correction


```{r}
ggplot(backpack) + 
  geom_histogram(aes(x = ratio, fill = backpain_labelled), bins = 20, col = "white") + 
  facet_grid(sex ~ backpain_labelled, 
             labeller = labeller(backpain_labelled = pain_labels, sex = sex_labels)) + 
  labs(x = "\n body weight: backpack weight ratio") +
      scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```






































